\section{Conclusion}

Searches of heavy resonances decaying into a pair of $Z$ boson to \llll final state are performed using
139~\ifb of 13~\tev~pp collision data collected by ATLAS experiment at the LHC.
The results are interpreted as 95\% CL upper limits on the production cross section of a spin-0 and spin-2 resonances under different theoretical models.
The search range of the hypothetical resonances is between 200~\gev~ to 2000~\gev~ depending on the signal model.

The spin-0 resonance is assumed to be a heavy Higgs like scalar produced predominantly from gluon–gluon fusion (ggF) and vector-boson fusion (VBF) decays, 
and it is studied under both the narrow-width approximation and with the large-width assumption.
For narrow-width approximation, the exclusion limits on cross section of heavy scalar decaying into two $Z$ bosons are set separately for ggF and VBF production modes, under MVA- and cut- based analysis.
In MVA-based analysis, the 95\% CL upper limit range is from 215 fb at $\mH = 240~\gev$ to 5.3 fb at $\mH = 2000~\gev$ for ggF production mode, 
and from 87 fb at $\mH = 255~\gev$ to 5.1 fb at $\mH = 1960~\gev$ for VBF production mode.
In cut-based analysis, the 95\% CL upper limit range is from 259 fb at $\mH = 245~\gev$ to 5.3 fb at $\mH = 2000~\gev$ for ggF production mode, 
and from 113 fb at $\mH = 240~\gev$ to 5.1 fb at $\mH = 2000~\gev$ for VBF production mode.
MVA-based analysis gains about 20\% improvement on upper limits at lower mass region comparing to the cut-based analysis, while for mass above 1500~\gev, both analyses perform closely.
For large-width approximation, limits are studied on ggF production rate at four different width assumptions: 1\%, 5\%, 10\% and 15\% of resonance's mass,
 with the interference between the heavy scalar and the SM Higgs boson as well as the heavy scalar and the SM \ggZZ continuum background taken into account.
The maximum and minimum of upper limits are obtained as 78 fb at $\mH = 400~\gev$ to 5.9 fb at $\mH = 2000~\gev$ for 1\% width;
98 fb at $\mH = 540~\gev$ to 6.4 fb at $\mH = 2000~\gev$ for 5\% width;
119 fb at $\mH = 540~\gev$ to 7.1 fb at $\mH = 2000~\gev$ for 10\% width;
133 fb at $\mH = 540~\gev$ to 7.5 fb at $\mH = 2000~\gev$ for 15\% width.
Last but not least, the framework of the Randall–Sundrum model with a graviton excitation spin-2 resonance with m($G_{KK}$) < 1500~\gev~ is excluded at 95\% CL.
