\section{Object and event selections}
\label{sec:hmhzz_selection}

\subsection{Object selections}
\label{sec:hmhzz_objsel}

Similar to VBSZZ analysis in section~\ref{sec:vbszz_selection}, the selection of this analysis relies on the definition of multiple objects: \textit{electrons}, \textit{Muons}, and \textit{jets}.
Details of definitions for each object are described as below:

\textbf{Electron:}
As described in section~\ref{sec:electron}, electrons are reconstructed from energy deposits in the EM calorimeter matched to a track in the inner detector.
The electron candidates satisfying the \textit{Loose} criterion from the likelihood-based (LH) method are selected,
with a selection efficiency ranging from 90\% for transverse momentum $\pt = 20~\gev$ to 96\% for $\pt > 60~\gev$.
In addition, the electrons are required to have $p_{T} > 7~\gev$, $|\eta| < 2.47$ and $|z_{0} sin\theta|$ < 0.5 mm.

\textbf{Muon:}
To increase the acceptance range in reco-level for \llll channel, all four types of muons
(CB, ST, CT, ME muons, described in section~\ref{sec:muon}) are used.
The CT muons are required to pass $p_{T} > 15~\gev$ and $|\eta| < 0.1$, while the ST muons are also limited in $|\eta| < 0.1$ region.
The ME muons are only used in the region of $2.5 < |\eta| < 2.7$.
And at most one CT, ST or ME muon is allowed in one \llll quadruplet.
The Muon candidates are required to pass $p_{T} > 5~\gev$ and $|\eta| < 2.7$,
and satisfy the \textit{Loose} identification criterion with an efficiency of at least 98.5\%.
The impact parameter requirements of $|d_{0}|$ < 1 mm and $|z_{0} sin\theta|$ < 0.5 mm are further applied.

\textbf{Jets:}
Jets are clustered using the anti-$k_t$ algorithm with radius parameter $R$ = 0.4 implemented in the \textsc{FastJet} package as described in section~\ref{sec:jet}. 
The `particle flow' (PFlow) objects~\cite{PERF-2015-09}, which combines measurements from both the tracker and the calorimeter, are used as inputs to the \textsc{FastJet} package.
The energy deposited in the calorimeter by all charged particles is removed, and the jet reconstruction is performed on an ensemble of PFlow objects
consisting of the remaining calorimeter energy and tracks which are matched to the hard interaction.
This improves the accuracy of the charged-hadron measurement, while retaining the calorimeter measurements of neutral-particle energies. 
Compared to only using topological clusters, jets reconstructed with the particle flow algorithm with $\pt > 30~\gev$ have approximately 10\% better transverse momentum resolution.
The jets used in this analysis are then required to have $\pt > 30~\GeV$ and $|\eta | < 4.5$.
To further reduce the effects of pile-up jets, a jet vertex tagger (JVT) is applied to jets with $p_{T} <$ 60~\gev~and $|\eta| < 2.4$.

\textbf{Overlap removal:}
As the selected jet and lepton candidates can be reconstructed from same detector information, an overlap-removal procedure is applied.
For electron and muon sharing the same ID track, the electron is selected in the case that the muon is calorimeter-tagged and does not have a MS track, or is a segment-tagged muon, otherwise the muon is selected.
The jet overlapping with electron (muon) within a cone of size of $\Delta R\equiv \sqrt{(\Delta \eta)^2 + (\Delta \phi)^2}= 0.2 (0.1)$ are removed.

%% ========================================================================
\subsection{Event selections}
\label{sec:hmhzz_eventsel}

First of all, the four-lepton events are required to pass single or multi-lepton triggers.
Due to the increasing of peak luminosity and pile-up, the \pt and \et thresholds of triggers increase slightly during the data-taking periods from 2015 to 2018.
Table~\ref{tab:hmhzz_triggers} summarizes the triggers used for \llll channel. 
The overall trigger efficiency for selected signal events passing final selection is around 98\%.

\begin{table}[!htbp]
\begin{center}
\caption{Summary of the $\pt$ ($E_T$) trigger thresholds (in~\gev) employed for the muon (electron) trigger selection in the year of 2015, 2016, 2017, and 2018.}
\label{tab:hmhzz_triggers}
\adjustbox{max width=\textwidth}{%
\vspace{0.2cm}
\begin{tabular}{|l|c|c|c|c|}
\hline
Trigger item& \multicolumn{4}{c|}{Trigger threshold}\\
& \multicolumn{1}{c|}{2015}& \multicolumn{1}{c|}{2016}& \multicolumn{1}{c|}{2017}& \multicolumn{1}{c|}{2018}\\
\hline
single muon&        $\mu 20$;~~$\mu 50$;~~$\mu 60$&
                    $\mu 24$;~~$\mu 26$;~~$\mu 40$;~~$\mu 50$&
                    $\mu 26$;~~$\mu 50$;~~$\mu 60$&
                    $\mu 26$;~~$\mu 50$;~~$\mu 60$\\
single electron&    $e24$;~~$e60$;~~$e120$&
                    $e26$;~~$e60$;~~$e140$;~~$e300$&
                    $e26$;~~$e60$;~~$e140$;~~$e300$&
                    $e26$;~~$e60$;~~$e140$;~~$e300$\\
\hline
dimuon&             $2\mu 10$;~~$\mu 18 \_\mu8$&
                    $2\mu 10$;~~$2\mu 14$;~~$\mu 22 \_\mu8$&
                    $2\mu 14$;~~$\mu 22 \_\mu8$&
                    $2\mu 14$;~~$\mu 22 \_\mu8$\\
dielectron&         $2e12$&
                    $2e15$;~~$2e17$&
                    $2e17$;~~$2e24$&
                    $2e17$;~~$2e24$\\
\hline
electron-muon&
                    $e24 \_\mu 8$&
                    $e24 \_\mu 8$;~~$e26 \_\mu 8$&
                    $e26 \_\mu 8$&
                    $e26 \_\mu 8$\\
                    $ $&
                    \multicolumn{4}{c|}{$e17\_\mu 14$;~~$e7 \_\mu24$;~~$2e12 \_\mu 10$;~~$e12 \_2\mu10$}\\
\hline

trimuon&
                    $\mu18\_2\mu4$&
                    $\mu11\_2\mu4$;~~$\mu6\_2\mu4$;~~$\mu 20\_2\mu 4$;~~$3\mu4$&
                    $4\mu4$;~~$\mu 20\_2\mu 4$;~~$3\mu4$&
                    $\mu 20\_2\mu 4$\\
                    $ $&
                    \multicolumn{4}{c|}{$3\mu6$}\\
\hline

trielectron&        $e17\_2e9$&
                    $e17\_2e9$;~~$e17\_2e10$&
                    $e24\_2e12$&
                    $e24\_2e12$\\

\hline

\end{tabular}}
\end{center}
\end{table}

The \llll quadruplets are formed by two opposite-sign, same-flavour (OSSF) lepton pairs ($\ell^{+}\ell^{-}$).
The $\pT$ threshold of first three leading leptons are required to be 20, 15 and 10~\gev.
If there are more than one combination of lepton pairing in quadruplet, the pairing is selected by keeping it with the mass of lepton pairs closest (leading pair, refers as $m_{12}$) and second closest (sub-leading pair, refers as $m_{34}$) to Z boson mass.
The mass of leading pair is required to satisfy $50 < m_{12} < 106~\gev$, while the sub-leading pair is required to be less than 115~\gev~ and larger than 50~\gev. 

The two lepton pairs in quadruplet are required to have angular separation with $\Delta R > 0.1$.
To suppress the contribution from $J/\psi \rightarrow \ell\ell$ decays, for $4\mu$ and $4e$ quadruplets, the events are rejected if any OSSF lepton pair is found with mass below 5~\gev.
If there are more than one quadruplets from different channels in event at this point, the one with highest expected signal rate is selected in the order of $4\mu$, $2e2\mu$, $4e$.
The transverse impact-parameter significance ($|d_0|/\sigma_{d_0}$) for muons (electrons) is then required to be smaller than 3 (5) to suppress the backgrounds from heavy-flavour hadrons.

In addition, the track- and calorimeter- based isolation criteria is required for all electrons and muons to further suppress the reducible backgrounds of \Zjet and \ttbar.
For lepton isolation selection, the two track- and calorimeter- based variables, $E_{T}^{topocone}$ and $p_{T}^{varcone}$ as described in section~\ref{sec:muon} (section~\ref{sec:electron}) for muons (electrons), are vulnerable to pileup.
For track-based variable, this is because of additional tracks in the event.
The definition of $p_{T}^{varcone}$ attempts to limit the tracks used in the calculation to those from the vertex via a loose cut of $|z_0\sin(\theta)| < 3$,
which proved to be too loose in new pile-up regime in 2017 and 2018 datasets.
So new track-based variable is used, 
by adding a requirement that the track be used in determining the vertex, or that, if not, it both passes the cut on $|z_0\sin(\theta)|$ and is not used in determining any other vertex,
which makes the track-based variable to be more isolation-robust in the high pile-up regime.
The new variable is named as ptvarcone[cone]$\_$TightTTVA$\_$pt[\pt cut], where [cone] is the cone size and [\pt cut] is the cutoff for including tracks in the calculation.

For calorimeter-based variable, the calculation of $E_{T}^{topocone}$ corrects the pile-up effects by subtracting an average pileup contribution computed over the whole detector.
But with the increasing of energy density of pile-up events, the root mean square (RMS) of $E_{T}^{topocone}$ variable increases,
which leads to the increment of possibility that the pile-up fluctuations are not be accounted for correctly.
One possible solution is using particle-flow (PFlow) method to calculate the calorimeter isolation.
As part of PFlow reconstruction process, it assigns the clusters to tracks which improves the track-cluster association for better determination of the raw value of the \et in the cone.
And using PFlow jets to calculate the pileup correction provides a further improvement.
So a resulting variable named neflowisol[cone] is used.
Finally, a requirement of isolation, called \textit{FixedCutPFlowLoose}, which gives better performance in high pile-up condition is applied to electrons and muons as: \\
	( max ( ptcone20\_TightTTVA\_pt500, ptvarcone30\_TightTTVA\_pt500 ) + 0.4 \times neflowisol20 ) / \pt < 0.16

On the top of impact parameter cut and lepton isolation cut, the four-lepton candidates are also required to originate from a common vertex to reduce \Zjet and \ttbar backgrounds.
This is ensured by applying a vertex fit $\chi^2$ cut of 4 ID tracks of lepton candidates satisfying $\chi^2 / N_{dof} < 6~(9)$ for events in 4$\mu$ (4$e$ and 2$e$2$\mu$) channel(s).

To improve the mass resolution, the QED process of final state radiation (FSR) photons in $Z$ boson decays are taken into account in the reconstruction of Z bosons.
The four-momentum of any reconstructed photon that is consistent with having been radiated from lepton(s) in leading pair are added into final state.
Moreover, the four-momenta of leptons in both (leading and sub-leading) pairs are recomputed by performing a Z-mass-constrained kinematic fit,
which uses a Breit Wigner $Z$ boson line-shape and Gaussian function with width set to the expected lepton resolution per lepton to model the momentum response function.
The Z-mass-constrained mass improves the $\mfl$ resolution by up to 15\% depending on $m_{H}$.

In summary, table~\ref{tab:hmhzz_selections} lists a comprehensive object and event level selection as described above.
%Table~\ref{tab:4l_cutflow_ggH600} to ~\ref{tab:4l_cutflow_VBFH1000} shows the cutflow of NWA ggF and VBF signal at the mass points of 600 and 1000~\gev~ as examples.

\begin{table}[!htbp]
  \centering
  \caption{Summary of the object and event selection requirements.
  \label{tab:hmhzz_selections}}
  \vspace{0.2cm}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{lccc}
      \hline\hline
      \multicolumn{4}{c}{\textbf \textsc{\textbf{Physics Objects}}} \\
      \hline\hline
      \multicolumn{4}{c}{\textsc{Electrons}} \\
      \multicolumn{4}{c}{Loose Likelihood quality electrons with hit in innermost layer, $\et > 7$~\GeV\ and $|\eta| < 2.47$} \\
      \multicolumn{4}{c}{Interaction point constraint: $|z_{0} \cdot \sin\theta| < 0.5$~mm}  \\
      \hline
      \multicolumn{4}{c}{\textsc{Muons}} \\
      \multicolumn{4}{c}{Loose identification with $\pt > 5$~\GeV\ and $|\eta| < 2.7$} \\
      \multicolumn{4}{c}{Calo-tagged muons with $\pt > 15$~\GeV\ and $|\eta| < 0.1$, segment-tagged muons with $|\eta| < 0.1$ } \\
      \multicolumn{4}{c}{Stand-alone and silicon-associated forward restricted to the $2.5 < |\eta| < 2.7$ region} \\
      \multicolumn{4}{c}{Combined, stand-alone (with ID hits if available) and segment-tagged muons with $\pt > 5$~\GeV} \\
      \multicolumn{4}{c}{Interaction point constraint: $|d_0| < 1$~mm and $|z_{0} \cdot \sin\theta| < 0.5$~mm (if ID track is available)} \\
      \hline
      \multicolumn{4}{c}{\textsc{Jets}} \\
      \multicolumn{4}{c}{anti-$k_T$ jets with \emph{bad-loose} identification, $\pt > 30 $~\GeV\ and $|\eta| < 4.5$} \\
      \hline
      \multicolumn{4}{c}{\textsc{Overlap removal}} \\
      \multicolumn{4}{c}{Jets within $\Delta R < 0.2$ of an electron or $\Delta R < 0.1$ of a muon are removed} \\
      \hline
      \multicolumn{4}{c}{\textsc{Vertex}} \\
      \multicolumn{4}{c}{At least one collision vertex with at least two associated track} \\

      \hline
      \multicolumn{4}{c}{\textsc{Primary vertex}} \\
      \multicolumn{4}{c}{Vertex with the largest $p_T^2$ sum} \\

      \hline\hline
      \multicolumn{4}{c}{\textbf \textsc{\textbf{Event Selection}}} \\
      \hline\hline
      \textsc{Quadruplet}     & \multicolumn{3}{l}{- Require at least one quadruplet of leptons consisting of two pairs of same-flavour} \\
      \textsc{Selection}      & \multicolumn{3}{l}{opposite-charge leptons fulfilling the following requirements:} \\
      & \multicolumn{3}{l}{- \pt~thresholds for three leading leptons in the quadruplet: $20, 15\text{ and } 10$~\GeV} \\
      & \multicolumn{3}{l}{- Maximum one calo-tagged or stand-alone muon or silicon-associated forward per quadruplet} \\
      & \multicolumn{3}{l}{- Leading di-lepton mass requirement: $50 < m_{12} < 106$~\GeV} \\
      & \multicolumn{3}{l}{- Sub-leading di-lepton mass requirement: $50 < m_{34} < 115$~\GeV} \\
      & \multicolumn{3}{l}{- $\Delta R(\ell,\ell')>0.10$ for all leptons in the quadruplet} \\
      & \multicolumn{3}{l}{- Remove quadruplet if alternative same-flavour opposite-charge} \\
      & \multicolumn{3}{l}{di-lepton gives $m_{\ell\ell} < 5$~\GeV} \\
      & \multicolumn{3}{l}{- Keep all quadruplets passing the above selection } \\
      \hline
      \textsc{Isolation}
      & \multicolumn{3}{l}{- Contribution from the other leptons of the quadruplet is subtracted} \\
      & \multicolumn{3}{l}{- FixedCutPFlowLoose WP for all leptons} \\
      \hline
      \textsc{Impact}         & \multicolumn{3}{l}{- Apply impact parameter significance cut to all leptons of the quadruplet} \\
      \textsc{Parameter}      & \multicolumn{3}{l}{- For electrons: $d_0/\sigma_{d_0}<5$} \\
      \textsc{Significance}   & \multicolumn{3}{l}{- For muons: $d_0/\sigma_{d_0}<3$} \\
      \hline
      \textsc{Best}           & \multicolumn{3}{l}{- If more than one quadruplet has been selected, choose the quadruplet} \\
      \textsc{Quadruplet}     & \multicolumn{3}{l}{ with highest Higgs decay ME according to channel: 4$\mu$, 2$e$2$\mu$, 2$\mu$2$e$ and 4$e$} \\
      \hline
      \textsc{Vertex}         & \multicolumn{3}{l}{- Require a common vertex for the leptons:} \\
      \textsc{Selection}      & \multicolumn{3}{l}{- $\chi^{2} / \mathrm{ndof} < 5$ for $4 \mu$ and $<9$ for others decay channels} \\
      \hline\hline
  \end{tabular}%
  }
\end{table}

\iffalse
\begin{table}[htbp]
  \centering
  \caption{Cutflow table for a narrow-width ggF signal sample at $\mH = 600~\GeV$. $N_{\text{event}}$ denotes the number
  of events selected after each cut is applied, normalized to $139~\ifb$, according to the expected upper limit on the
  cross section. The acceptances (the proportion of events selected relative to the initial number of events) are also
  included.}
  \label{tab:4l_cutflow_ggH600}

  \adjustbox{max width=\textwidth}{%
  \begin{tabular}{
      l S[table-format=2.2] S[table-format=4.1] S[table-format=3.2] S[table-format=1.3]}
    \toprule

    ~ & {$N_{\text{event}}$}  & {$N_{\text{event}}$/BR($ZZ\to\llll$)} & {Acc. [\%]}  & {Acc. $\cdot$ BR($ZZ\to\llll$) $\cdot$ 1000}  \\
    \midrule
    Initial              &  17.902  &  3964.3  &  100.00  &  4.516  \\
    Lepton selection     &   6.247  &  1383.4  &   34.90  &  1.576  \\
    SFOS                 &   5.758  &  1275.1  &   32.16  &  1.453  \\
    Kinematic cuts       &   5.754  &  1274.2  &   32.14  &  1.452  \\
    $Z_1$ Mass           &   5.726  &  1267.9  &   31.98  &  1.444  \\
    $Z_2$ Mass           &   5.112  &  1132.0  &   28.56  &  1.290  \\
    $J/\psi$ Veto        &   5.111  &  1131.9  &   28.55  &  1.289  \\
    $\Delta R$           &   5.111  &  1131.7  &   28.55  &  1.289  \\
    Isolation            &   4.864  &  1077.0  &   27.17  &  1.227  \\
    Impact parameters    &   4.796  &  1062.1  &   26.79  &  1.210  \\
    Vertex requirement   &   4.786  &  1059.8  &   26.73  &  1.207  \\
    Trigger              &   4.783  &  1059.1  &   26.72  &  1.207  \\
    ``Badjet'' veto      &   4.763  &  1054.7  &   26.61  &  1.201  \\
    \bottomrule
  \end{tabular}
  }
\end{table}


\begin{table}[htbp]
  \centering
  \caption{Cutflow table for a narrow-width ggF signal sample at $\mH = 1000~\GeV$. $N_{\text{event}}$ denotes the number
  of events selected after each cut is applied, normalized to $139~\ifb$, according to the expected upper limit on the
  cross section. The acceptances (the proportion of events selected relative to the initial number of events) are also
  included.}
  \label{tab:4l_cutflow_ggH1000}

  \adjustbox{max width=\textwidth}{%
  \begin{tabular}{
      l S[table-format=2.2] S[table-format=4.1] S[table-format=3.2] S[table-format=1.3]}
    \toprule

    ~ & {$N_{\text{event}}$}  & {$N_{\text{event}}$/BR($ZZ\to\llll$)} & {Acc. [\%]}  & {Acc. $\cdot$ BR($ZZ\to\llll$) $\cdot$ 1000}  \\
    \midrule
    Initial              &  5.603  &  1240.8  &  100.00  &  4.516  \\
    Lepton selection     &  2.141  &   474.1  &   38.21  &  1.725  \\
    SFOS                 &  1.944  &   430.5  &   34.70  &  1.567  \\
    Kinematic cuts       &  1.943  &   430.3  &   34.68  &  1.566  \\
    $Z_1$ Mass           &  1.932  &   427.8  &   34.48  &  1.557  \\
    $Z_2$ Mass           &  1.715  &   379.7  &   30.61  &  1.382  \\
    $J/\psi$ Veto        &  1.715  &   379.7  &   30.60  &  1.382  \\
    $\Delta R$           &  1.714  &   379.6  &   30.60  &  1.382  \\
    Isolation            &  1.640  &   363.2  &   29.27  &  1.322  \\
    Impact parameters    &  1.620  &   358.6  &   28.90  &  1.305  \\
    Vertex requirement   &  1.616  &   357.8  &   28.84  &  1.302  \\
    Trigger              &  1.615  &   357.7  &   28.83  &  1.302  \\
    ``Badjet'' veto      &  1.609  &   356.2  &   28.71  &  1.297  \\
    \bottomrule
  \end{tabular}
  }
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Cutflow table for a narrow-width VBF signal sample at $\mH = 600~\GeV$. $N_{\text{event}}$ denotes the number
  of events selected after each cut is applied, normalized to $139~\ifb$, according to the expected upper limit on the
  cross section. The acceptances (the proportion of events selected relative to the initial number of events) are also
  included.}
  \label{tab:4l_cutflow_VBFH600}

  \adjustbox{max width=\textwidth}{%
  \begin{tabular}{
      l S[table-format=2.2] S[table-format=4.1] S[table-format=3.2] S[table-format=1.3]}
    \toprule

    ~ & {$N_{\text{event}}$}  & {$N_{\text{event}}$/BR($ZZ\to\llll$)} & {Acc. [\%]}  & {Acc. $\cdot$ BR($ZZ\to\llll$) $\cdot$ 1000}  \\
    \midrule
    Initial              &  12.143  &  2688.9  &  100.00  &  4.516  \\
    Lepton selection     &   4.307  &   953.7  &   35.47  &  1.602  \\
    SFOS                 &   3.975  &   880.2  &   32.74  &  1.478  \\
    Kinematic cuts       &   3.972  &   879.6  &   32.71  &  1.477  \\
    $Z_1$ Mass           &   3.953  &   875.4  &   32.56  &  1.470  \\
    $Z_2$ Mass           &   3.545  &   785.0  &   29.19  &  1.318  \\
    $J/\psi$ Veto        &   3.545  &   785.0  &   29.19  &  1.318  \\
    $\Delta R$           &   3.544  &   784.9  &   29.19  &  1.318  \\
    Isolation            &   3.418  &   756.9  &   28.15  &  1.271  \\
    Impact parameters    &   3.368  &   745.9  &   27.74  &  1.253  \\
    Vertex requirement   &   3.362  &   744.5  &   27.69  &  1.250  \\
    Trigger              &   3.360  &   744.0  &   27.67  &  1.250  \\
    ``Badjet'' veto      &   3.340  &   739.7  &   27.51  &  1.242  \\
    \bottomrule
  \end{tabular}
  }
\end{table}


\begin{table}[htbp]
  \centering
  \caption{Cutflow table for a narrow-width VBF signal sample at $\mH = 1000~\GeV$. $N_{\text{event}}$ denotes the number
  of events selected after each cut is applied, normalized to $139~\ifb$, according to the expected upper limit on the
  cross section. The acceptances (the proportion of events selected relative to the initial number of events) are also
  included.}
  \label{tab:4l_cutflow_VBFH1000}

  \adjustbox{max width=\textwidth}{%
  \begin{tabular}{
      l S[table-format=2.2] S[table-format=4.1] S[table-format=3.2] S[table-format=1.3]}
    \toprule

    ~ & {$N_{\text{event}}$}  & {$N_{\text{event}}$/BR($ZZ\to\llll$)} & {Acc. [\%]}  & {Acc. $\cdot$ BR($ZZ\to\llll$) $\cdot$ 1000}  \\
    \midrule
    Initial              &  3.827  &  847.4  &  100.00  &  4.516  \\
    Lepton selection     &  1.474  &  326.5  &   38.53  &  1.740  \\
    SFOS                 &  1.351  &  299.1  &   35.30  &  1.594  \\
    Kinematic cuts       &  1.350  &  299.0  &   35.28  &  1.593  \\
    $Z_1$ Mass           &  1.341  &  297.0  &   35.04  &  1.583  \\
    $Z_2$ Mass           &  1.195  &  264.6  &   31.23  &  1.410  \\
    $J/\psi$ Veto        &  1.195  &  264.6  &   31.23  &  1.410  \\
    $\Delta R$           &  1.195  &  264.6  &   31.22  &  1.410  \\
    Isolation            &  1.161  &  257.1  &   30.34  &  1.370  \\
    Impact parameters    &  1.148  &  254.1  &   29.99  &  1.354  \\
    Vertex requirement   &  1.146  &  253.8  &   29.95  &  1.352  \\
    Trigger              &  1.145  &  253.6  &   29.93  &  1.352  \\
    ``Badjet'' veto      &  1.139  &  252.2  &   29.77  &  1.344  \\
    \bottomrule
  \end{tabular}
  }
\end{table}
\fi
\input{chapters/HMHZZ/cate}
