% !TeX root = ../main.tex

\begin{abstract}
论文介绍了本人在粒子物理领域基于大型强子对撞机（LHC）上ATLAS 实验做的研究工作。 
LHC是当今世界上最大的、能量最高的对撞机，在其上发生的质子-质子对撞实验质心系能量最高可达14~\tev。
LHC凭借其空前的能量，在理论与实验之间架起了一座重要桥梁。
ATLAS实验是LHC上的一个通用粒子探测器实验，同时也是体积最大的粒子探测器。
该实验旨在利用LHC提供的超高能量和亮度来观测涉及大质量粒子的物理现象，而这些粒子是使用早期的低能加速器所无法观察到的。
同时，ATLAS实验也是2012年7月LHC上参与发现希格斯粒子的两个重要实验之一。

本文基于ATLAS实验在LHC上收集到的亮度为139~\ifb~能量为13~\tev~的质子-质子对撞数据，重点介绍了两个$Z$玻色子衰变到四轻子末态过程的一系列研究。
包括，标准模型（SM）下$ZZ$到四轻子过程截面的测量、矢量玻色子散射（VBS）过程在$ZZ$到四轻子末态的观测。
首先，$ZZ$到四轻子过程截面的测量结果为$\sigma_{ZZjj}^{tot} = 1.27 \pm 0.12 (\mathrm{stat}) \pm 0.02 (\mathrm{theo}) \pm 0.07 (\mathrm{exp}) \pm 0.01 (\mathrm{bkg}) \pm 0.03 (\mathrm{lumi})~[fb]$，
总体相对误差为11\%。
在误差范围内，该结果和标准模型预言值$1.14 \pm 0.04 (\mathrm{stat}) \pm 0.20 (\mathrm{theo})~[fb]$相吻合。
同时，在两个$Z$玻色子伴随着两个喷注（jets）末态的电弱相互作用过程的寻找中， 我们观测到偏离本底假说超过5倍标准差（5.5 $\sigma$) 的明显偏差。
在此基础上，本文也介绍了使用3000~\ifb~模拟数据，质心能量为14~\tev~的高亮度大型强子对撞机（HL-LHC）产生 EW-$ZZjj$ 过程的前景研究，
预言将可以观测到大于7倍标准差（7 $\sigma$) 的明显偏差。

本文还介绍了在一对$Z$玻色子衰变至四轻子末态过程中寻找重共振态的实验。根据不同的信号模型，寻找的粒子质量区间设置在200~\gev~ 到 2000~\gev~之间。
基于该测量结果，没有证据可以证明重共振态的存在。因此，研究给出了基于不同信号模型的截面上限，包括在不同衰变宽度假说下自旋为0的共振态，以及基于Randall–Sundrum模型的自旋为2的引力子（graviton）。
在该分析中，我们认为，信号主要可通过gluon-gluon Fusion (ggF) 和Vector Boson Fusion (VBF) 过程产生。
在自旋为0的窄衰变宽度模型下，我们对ggF 和VBF两个过程都进行了研究。而对于大宽度模型，由于在质量很高的区间分辨率很差以及VBF过程的统计量太小等客观原因，只对ggF过程进行了研究。
对于自旋为2的模型，实验给出了Randall–Sundrum模型的引力子的理论质量下限，为1500~\gev。

本文所介绍的$ZZ$玻色子衰变到四轻子末态过程的结果都与标准模型预测的一致。
该结果完善了Vector Boson Scattering 过程在各个衰变末态的观测，是对电弱对称性坏研究的新的里程碑。
同时，没有发现明显的超标准模型新物理过程。
我们期待，大大提高了亮度和能量的下一代高亮度大型强子对撞机（HL-LHC）实验能够为这些新物理过程的寻找带来更高的灵敏度，和对如四轻子末态这样的罕见物理过程更精确的测量。
\end{abstract}

\begin{enabstract}
This dissertation presents my research in the field of Particle Physics with the ATLAS experiment at the Large Hadron Collider (LHC). 
The LHC is the largest and most powerful collider in the world, and it is the proton-proton collider with the centre-of-mass energy up to 14~\tev.
With its unprecedented energy, the LHC was built as a bridge between the theories and the experiment.
The ATLAS experiment is a general-purpose particle detector experiment with the largest volume at the LHC.
The experiment was designed to take advantage of the extramely high energy and luminosity available at the LHC 
and observe phenomena that involve highly massive particles which were not observable using earlier lower-energy accelerators.
And it was one of the two LHC experiments involved in the discovery of the Higgs boson in July 2012.

This dissertation focus on the studies with two $Z$ bosons production decaying into \llll final state, where $\ell$ stands for electron or muon, using 139~\ifb of 13~\tev~proton-proton (pp) collision data collected by ATLAS experiment at the LHC.
The $ZZ$ production in \llll channel provides a most clean and sensitive tool to test the Standard Model (SM) at the energy frontier and to study the \textit{Higgs} physics.
First of all, studies including the measurement on SM $ZZjj$ production cross section and the observation of Vector Boson Scattering (VBS) process.
%as well as the searches of heavy resonances in $ZZ$ production decaying into \llll final state are reported in this dissertation.
The fiducial cross section for SM $ZZjj$ production is measured to be 
    $\sigma_{ZZjj}^{tot} = 1.27 \pm 0.12 (\mathrm{stat}) \pm 0.02 (\mathrm{theo}) \pm 0.07 (\mathrm{exp}) \pm 0.01 (\mathrm{bkg}) \pm 0.03 (\mathrm{lumi})~[fb]$
    with a total relative uncertainty of 11\% for the \llll final state, and found to be compatible with the SM prediction of $1.14 \pm 0.04 (\mathrm{stat}) \pm 0.20 (\mathrm{theo})~[fb]$.
The electroweak production of two jets in association with a Z-boson pair (EW-$ZZjj$) is observed with
a significant deviation from the background-only hypothesis corresponding to a statistical significance of 5.5 $\sigma$.
Following with the observation, the prospect study for the EW-$ZZjj$ production at the High luminosity LHC (HL-LHC) using 3000~\ifb simulated pp collision data at a centre-of-mass energy of 14~\tev~is presented,
with a expected significance of around 7 $\sigma$.

Meanwhile, a search for heavy resonances decaying into a pair of $Z$ bosons to \llll final state is also conducted in this dissertation.
Different mass ranges for the hypothetical resonances are considered, depending on the signal models and spanning between 200~\gev~and 2000~\gev.
Data is found to agree with a background-only hypothesis, thus, the results are interpreted as upper limits on production cross section for sevaral different models, 
including heavy Higgs like (spin-0) narrow-width approximation (NWA) and large-width approximation (LWA), as well as the Randall–Sundrum model with a graviton excitation spin-2 resonance (RSG).
The signal is assumed to generate dominatly via gluon-gluon Fusion (ggF) production mode and Vector Boson Fusion (VBF) production mode.
Both ggF and VBF channels are studied in NWA, while for LWA, only ggF channel is studied due to worse resolution in higher mass region and the lack of statistic for VBF process.
In addition, mass of RS Graviton is constrained, m($G_{KK}$) < 1500~\gev~ is excluded at 95\% CL by $ZZ \rightarrow \llll$ analysis.

The ZZ to \llll production presented in this dissertation are consistent with the SM prediction. 
This result completes the observation of weak boson scattering that is a new milestone in the study of electroweak symmetry breaking. 
In the meantime, no indication of new physics is observed. 
We are looking forward to the HL-LHC, with greatly increased luminosity and higher centre-of-mass energy, which should enhance the sensitivity for new physics search and precise measurement for rare process.
\end{enabstract}
