% !TeX root = ../main.tex

\begin{acknowledgments}

First of all, I would like to express my great gratitude to my supervisors Prof. Zhao Zhengguo and Dr. Ma Hong, for their guidance and patience during my Ph.D years.
It's Zhengguo, who inspire me with his deep physics insight when I was an undergraduate student and lead me enter the field of Particle Physics.
I will never forget how I was attracted by his broad knowledge and the amazing picture of particles he showed me, which became the reason I choose the Particle Physics as my major.
It's always relaxed and benifit greatly when chating with him, which broads my version, makes me to be more confident and helps me step out of so many difficulties.

Thanks Hong, for giving me the oppotunity to study in Brookhaven National Lab (BNL) that I can work with so many senior and brilliant physicist, and teaching me a lot in the details of physics.
As the chair of physics department at BNL, can you imagine that he managed to take time sitting with me every week, teaching me the details and techniques of my analysis
as well as helping me to parepre my talks at conference.

Thank you both for leading me to the field of physics, showing me how beautiful the science and the world are. 
And thank you for providing me so many oppotunities and tremendous supports to work at physics frontier and work with people all over the world.
It's my greatest honor to be your student.
Your strong personalitis will difinately influence my future life and career.

I would like to give my large gratitude to Prof. Zhou Bing.
It's Bing who introduced me to ATLAS experiment when I was a junior. 
As a professor and group leader of ATLAS group in University of Michigan with busy schedule, 
Bing still took time to teach me in physics start from simple formulas and help me to prepare my first academic presentation patiently when I was a undergraduate student.
Also it's my great fortunate that I can have opportunities to work with you and learn from you in so many analyses during these years.
Your kind and patience, your high standard influence me deeply in all these years.

Moreover, I really want to give my sincere gratitude to Dr. Xu Lailin.
Thank you, Lailin, for all your helps during the passing five years.
Thanks for teaching me in all the analysis details, coding techniques, presentation skills hand by hand.
You are really a very good and patient teacher and gives me as many knowledges as you accompany.
Your broad knowledge, your perseverance in science and your very hard working indeed affect me a lot.

In the meantime, I want to give my special thanks to Dr. Li Bing, who helped me a lot in several different analyses 
(low-mass 4$\mu$ resonance search, VBSZZ analysis, $Z'$ search), he never hesitate to give his hand to me when I faced difficulties.

I would like to express my gratitude to many colleagues in both USTC and BNL team.
Thanks Prof. Sun Yongjie, who is the supervisor of my undergraduate thesis, helped me start my first detector project on MRPC. 
Also thanks Dr. Liu Zhen who teached me in details in this project, and helped me a lot for my life at BNL too.
Thanks Prof. Peng Haiping, Prof. Zhu Yingchun and Dr. Hu Qipeng for helping me all the details and techniques in HWW analysis when I was a biginner.
Thanks Dr. Dai Tiesheng, I have learnt quite a lot in the project of Monitored Drift Tubes (MDT) when working with you at CERN and also thank you for all the helps in regular life since that was my first time to Europe.
Thanks Dr. Chen Hucheng, who is the supervisor of my ATLAS qualification task on LAr Trigger Digitizer Boards (LTDB) and the person lead me into this interesting electronic project.
And my appreciate to Dr. Xu Hao, Dr. Chen Kai and Dr. Liu Hongbin that teached me in patience for this project as I was really a freshman on electronics.
Thanks Prof. Yuji Enari and Dr. Georges Aad for the helps in LAr software tasks when I moved from BNL to CERN.
In the meantime, I would really like to give my gratitude to Dr. Michael Begal, Dr. Marc-Andre Pleier, Dr. Alessandro Tricoli, Dr. George Redlinger, Dr. Viviana Cavaliere, Dr. Gaetano Barone and many senior physicist in BNL omaga group. I have learnt a lot from every chat with you and every seminar you hosted.
Also I want to thanks Prof. Wu Yusheng, Prof. Qian Jianming, Prof. Liu Yanwen, Dr. Ju Xiangyang for teaching me in lots of details in different physics analyses.

Moreover, I want to give my thanks to friends I met at USTC, BNL and CERN during my Ph.D years.
Thanks Dr. Yang Qian, Dr. Chu Xiaoxuan, Dr. Tu Biao, Dr. Gao Shanshan, Dr. Liu Feng, Dr. Yuan Guangyuan, and many other friends I met at BNL. 
Thanks Dr. Geng Cong, Dr. Li Peilian, Dr. Zhang Liqing, Dr. Guo Yicheng, Dr. Xu Tairan, Dr. Wang Rongkun, Chen Jing, He Fudong, Guo Qianying, Chen Ye, Xu Hao, Wang Tao, Xie Xiangyu, Liu Xiangtian and all friends I met at USTC and CERN. 
Thank you all my friends! I will always remember all the happiniess with you, and best wishes to you in the future!

Last but not least, I would give my greatest gratitude to my families. Thanks my parents to give me all your endless loves and supports in my whole life.
My deep appreciate to my three aunts for loving and caring me so much since I was born and help me to accompany with my mother when I was thousands miles far away from home.
And my husband, Lin, thank you for your understanding and walk through all difficulties with me in these years especially when we were in a foreign country.

\end{acknowledgments}
