% !TeX root = ../main.tex

\begin{publications}

\section*{已发表论文}

\begin{enumerate}
    \item ATLAS Collaboration. Search for electroweak diboson production in association with a high-mass dijet system in semileptonic final states in pp collisions at 13TeV with the ATLAS detector[J]. \textbf{Phys. Rev. D 100, 032007}.
    \item ATLAS Collaboration. Constraints on off-shell Higgs boson production and the Higgs boson total width in $ZZ \rightarrow \llll$ and $ZZ \rightarrow \llvv$ final states with the ATLAS detector[J]. \textbf{Physics Letters B, 2018, 786}.
    \item ATLAS Collaboration. Measurement of the four-lepton invariant mass spectrum in 13~\tev~ proton-proton collisions with the ATLAS detector[J]. \textbf{Journal of High Energy Physics, 2019, 2019(4): 48}.
    \item Chen K, et al. Design and Evaluation of the LAr Trigger Digitizer Board in the ATLAS Phase-I Upgrade[J]. \textbf{IEEE Transactions on Nuclear Science, 2019, 66(8): 2011-2016}.
\end{enumerate}

\section*{待发表论文}

\begin{enumerate}
    \item Observation of electroweak production of two jets and a Z-boson pair with the ATLAS detector at the LHC. \textbf{Submitted to Nature Physics, e-print: arXiv:2004.10612}.
    \item Search for heavy resonances decaying into a pair of Z bosons in $ZZ \rightarrow \llll$ and $ZZ \rightarrow \llvv$ final states using 139~\ifb~ of pp collisions at 13~\tev~ with the ATLAS detector. \textbf{Submitted to Eur. Phy. J. C, e-print: arXiv:2009.14791}.
\end{enumerate}

\section*{会议报告}
\begin{enumerate}
    \item Search for heavy resonances decaying into a pair of Z bosons with the ATLAS Detector. \textbf{China LHC Physics Workshop, online (Beijing, China), 2020.11}
    \item Measurement of Inclusive \llll and \llvv + 2-jet Cross Section and Observation of EW Component with the ATLAS detector. \textbf{Workshop on Connecting Insights in Fundamental Physics: Standard Model and Beyond, Corfu, Greece, 2019.9}
    \item Off-shell Higgs signal strength measurement in the high-mass $ZZ \rightarrow \llll$ and $ZZ \rightarrow \llvv$ final states with the ATLAS detector. \textbf{American Physics Society April Meeting, Columbus, USA, 2018.4}
\end{enumerate}

\end{publications}
