\chapter{Summary}

On December 3rd, 2018, the LHC finished its second run (run-2) after three fantastic years.
Thanks to run-2 with large increase in statistics, we now know the masses of the Higgs boson, top quark and W boson to considerably greater precision,
and also confirm the Standard Model as a stable theory.

In this dissertation, various physics processes in $ZZ \rightarrow \llll$ final state are studied, taking the advantage of full run-2 pp collision data in the LHC.
Using this signature, we measured the fiducial cross section of $ZZ$ production to \lllljj channel in SM, which is an important physics process and major background in many analysis with $ZZ$ production, eg. Higgs analysis ($HZZ$).
In addition, we searched the electroweak $ZZ$ production via vector boson scattering in associated with 2-jet process in \llll final state.
In the meantime, the searches of heavy resonances decaying into a pair of $Z$ bosons to \llll final state for several different hypothetical resonances are conducted in this dissertation.
The results of several analyses are summarized as below:

\textbf{Measurement of fiducial cross section of $ZZ$ production in \lllljj final state}

The fiducial cross section of inclusive SM $ZZ \rightarrow \llll$ production is measured to be:
\begin{equation}
	\sigma^{fid}_{ZZ\rightarrow\llll} = 1.27 \pm 0.12 (stat) \pm 0.02 (theo) \pm 0.07 (exp) \pm 0.01 (bkg) \pm 0.03 (lumi)~ [fb]
\end{equation}
which is found to be compatible with the SM prediction.
The $ZZ$ cross section is calculated with up to one (three) outgoing partons at NLO (LO) using \textsc{Sherpa} 2.2.2 for QCD production,
and in LO using \MGMCatNLO~2.6.1 for EW production.
The total uncertainty is 11\%, the analysis is still data statistic dominant (data statistic uncertainty is about 9.5\%).

\textbf{Observation of electroweak $ZZ$ production in \lllljj final state}

Thanks to the largely increased data statistic collected by ATLAS experiment in the LHC run-2, 
the electroweak $ZZ$ production (EW-$ZZjj$) to \llll channel in association with two jets is observed with a significant deviation from the background-only hypothesis.
The signal strength of EW-$ZZjj$ production, the normalization of QCD-$ZZjj$ production, as well as the observed and expected statistical significance measured in \lllljj channel are found to be:
\begin{equation}
\begin{split}
	\mu_{\mathrm{EW}} = 1.54 \pm 0.42 \\
	\mu_{\mathrm{QCD}} = 0.95 \pm 0.22 \\
	\text{Obs. (Exp.) Significance} = 5.48~(3.90)~\sigma
\end{split}
\end{equation}

Then in this dissertation, the differential cross section and expected significance of EW-$ZZjj$ production, 
using 3000~\ifb~simulated pp collision data at a centre-of-mass energy of 14~\tev~to be recorded by ATLAS experiment at the HL-LHC,
are studied via simulations.
The HL-LHC will for sure give us more opportunity to probe rare process like $ZZ \rightarrow \llll$ in the future.

\textbf{Searches of heavy $ZZ$ resonances in \llll final state}

Searches of heavy $ZZ$ resonances are performed in four-lepton invariant mass \mfl range from 200~\gev~to 2000~\gev.
Data are found to agree with the background-only hypothesis, and 95\% CL upper limits are set on the production rate under the models of:
\begin{itemize}
	\item Spin-0 heavy Higgs under narrow-width approximation (NWA). \\
Search range is from 200~\gev~ to 2000~\gev.\\
In DNN-based analysis, the limits range from 215 fb at $\mH = 240~\gev$ to 5.3 fb at $\mH = 2000~\gev$ for ggF production mode,
and from 87 fb at $\mH = 255~\gev$ to 5.1 fb at $\mH = 1960~\gev$ for VBF production mode.\\
The DNN-based analysis is found to be at most 20\% better than cut-based results.
	\item Spin-0 heavy Higgs under large-width approximation (LWA) with the width of 1, 5, 10, 15\% of its mass.\\
Search range is from 400~\gev~ to 2000~\gev, and only ggF production is studied.\\
The maximum and minimum of upper limits are obtained as 78 fb at $\mH = 400~\gev$ to 5.9 fb at $\mH = 2000~\gev$ for 1\% width;
98 fb at $\mH = 540~\gev$ to 6.4 fb at $\mH = 2000~\gev$ for 5\% width;
119 fb at $\mH = 540~\gev$ to 7.1 fb at $\mH = 2000~\gev$ for 10\% width;
133 fb at $\mH = 540~\gev$ to 7.5 fb at $\mH = 2000~\gev$ for 15\% width.
	\item Spin-2 graviton excitation under the Randall–Sundrum model.\\
Search range is from 600~\gev~ to 2000~\gev, and only ggF production is studied.\\
The maximum and minimum of limits are 73 fb at $\mH = 600~\gev$ and 5.6 fb at $mH = 1880~\gev$ for ggF production mode.
And the mass of graviton below 1500~\gev~ is excluded comparing the observed results with theoretical prediction.
\end{itemize}
~~

In summary, the $ZZ \rightarrow \llll$ production presented in this dissertation are consistent with SM prediction.
This result completes the observation of weak boson scattering that is a new milestone in the study of electroweak symmetry breaking.
In the meantime, no indication of new physics is observed.
We are looking forward to the HL-LHC, with greatly increased luminosity and higher centre-of-mass energy, 
which should enhance the sensitivity for new physics search and precise measurement for rare process like \llll final state.
